### 2013-09-18 chi2014/method.tex

Initially, workers were randomly paired with a question from a pool of questions. However, we eventually dropped all other questions, so workers would only receive the MP3 player question. When testing multiple questions, we attempted to prevent workers from answering the same question twice (for example, if they chose the HIT requesting 10 responses, then the HIT requesting 20 responses) . However, we were not always successful in preventing this from happening. Thus, we only use a worker's first set of responses if they answered the question multiple times.

@@

Initially, we sought 10 HITs for each condition. However, we found that collecting only 10 HITs for the lower response conditions (5, 10, 20 responses) limited our ability to make meaningful comparisons between responses received from the larger response conditions (50, 75, 100). Accordingly, we sought to receive a minimum of 400 ideas for each condition. We found the 5 and 10 conditions to be particularly unpopular, and were not able to fully reach the desired number of ideas in these conditions.

@@

To analyze the data, we organized it into sets hierarchical clusters, where the clusters encode similarity relationships between ideas. Specifically, parent nodes are more generalized versions of child nodes. This clustering enables a wide range of data analysis. We introduce specific terminology, then describe the clusters and the process used to create them.

@@

@@

The primary author clustered the 3007 response instances into ideas and category trees. A researcher not involved in the project randomly sampled 40 category trees to assess whether ideas within the tree should be there, and whether parent-child relationships correctly encoded generalizations of concepts. Results indicate that 8\% of the data would be X by the independent researcher, and 0.7\% of the data would be Y by the independent researcher.

>>>>

Initially, workers were randomly paired with a question from a pool of questions. However, we eventually dropped all other questions, so workers would only receive the MP3 player question. %When testing multiple questions, we attempted to prevent workers from answering the same question twice (for example, if they chose the HIT requesting 10 responses, then the HIT requesting 20 responses) . However, we were not always successful in preventing this from happening. Thus, we only use a worker's first set of responses if they answered the question multiple times.

@@

Initially, we sought 10 HITs for each condition. However, we found that collecting only 10 HITs for the lower response conditions (5, 10, 20 responses) limited our ability to make meaningful comparisons between responses received from the larger response conditions (50, 75, 100). Accordingly, we sought to receive a minimum of 400 ideas for each condition. We found the 5 and 10 conditions to be particularly unpopular, and were not able to reach this minimum.

@@

To analyze the data, we organized it into sets hierarchical clusters, where the clusters encode similarity relationships between ideas. Specifically, parent nodes are more generalized versions of child nodes. This clustering enables a wide range of data analysis. We introduce specific terminology, motivate the technique, then describe the clusters and the process used to create them.

@@

\subsubsection{Clustering: Motivation}

Initially, a coding scheme was employed in which a master list of unique ideas was formed, and each response was assigned a categorical code from this list. It proved difficult to determine and adhere to a constant granularity of distinction. For example, it is desireable to encode some equality between "use [MP3 players] to build a chair, and "use [MP3 players] to build a table". Information loss results from either assigning both the same code or each different codes. An interval specificity scale is also difficult to employ; intuitively, we cannot compare the distance between "audiobooks" and "audio books for the blind" with the distance between the latter and "[audio] instructions for the blind on a variety of things".

A category tree allows the encoding of generalization relationships such that useful metrics can be extracted without any assumptions about distance.
For example, The number of descendants of an idea gives a measure of how broadly that node was explored. 
The prevalance of similar responses can be approximated at multiple levels; the number of instances under a tree represents the popularity of a category, while the same for an individual node provides a weighted score of ideas that are exactly equivalance.
An idea can be considered more closely related to its adjacent ideas than it is to all other ideas in the tree.
Using this common structure to operationalize originality and uniqueness ensures consistency in analysis. Furthermore, the category forest relies primarily on generalization decisions for construction, which are more clearly defined than equivalence.

@@

The primary author clustered the 3007 response instances into ideas and category trees. A researcher not involved in the project randomly sampled 40 category trees to assess whether ideas within the tree should be there, and whether parent-child relationships correctly encoded generalizations of concepts. 10\% (HDI 6-14) of instances were marked as specific than their associated idea. 0.7\% (HDI 1.3-2.8\%) of instances were marked as not generalized by their parents. No significant effect was found between conditions for probability of either error.
